---
title: "R Notebook"
output: html_notebook
---
```{r}
getwd()
library(fUnitRoots)
library(fGarch)
library(rugarch)
```

```{r}
daily <- as.numeric(read.csv("daily_2009_to_2021.csv",header=T, stringsAsFactors=F)$Close)
plot(daily,type="l", main="Nifty50 daily prices from 2009 to oct 2021", xlab = "", ylab = "dialy prices")
daily_return= diff(log(daily))*100
plot(daily_return,type="l", main="Nifty50 daily log returns from 2009 to oct 2021", xlab = "", ylab = "dialy log returns")
train0918 = daily_return[1:2439]
valid19 = daily_return[2440:2680]
train0920 = daily_return[1:2930]
valid21 = daily_return[2931:3149]
```

```{r}
acf(train0918,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0918,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0918,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0918) #p-value = 0.01
```

```{r}
ar=arima(train0918,order=c(9,0,0),  fixed=c(NA,0, 0, 0, 0, 0, 0, 0,NA, NA))
ar

Box.test(ar$residuals,lag=10,type="Ljung")
pv=1-pchisq(11.594,8)
pv#0.1702585

forecast=predict(ar,241)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred
print(sqrt(sum((valid19-E1)^2)/241))

E1=forecast$pred
print(sqrt((sum(valid21[1:45]-E1)^2)/45))

plot(1:241,valid19,type="l",main="daily 2009-2018 AR(9) Forecasting", col="black", xlab = "", ylab="")
lines(1:241, E1, type="l", col="red")
lines(1:241, U1, type="l", col="blue")
lines(1:241, L1, type="l", col="blue")
legend(x="topleft",lty=c(1,1),pch=c(1,1),c("True returns","prediction"),col=c("black","red"))

#plot(2000:2680,train0918[2000:2680],type="o",main="Forecasting")
#lines(2439:2680, append(train0918[2439],E1),type="o",col="red")
#lines(2439:2680, U2,type="l",col="blue")
#lines(2439:2680, L2,type="l",col="blue")
#legend(x="topleft",c("True returns","prediction"),col=c("black","red"))
```

```{r}
ar_res = (ar$residuals)^2
acf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
pacf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(ar_res,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(ar_res) #p-value = 0.01
```
```{r}
garch_ar=garchFit(train0918~arma(1, 0)+garch(1,1),data=train0918,trace=F)
summary(garch_ar)
garch_ar_resi=residuals(garch_ar,standardize=T)
plot(garch_ar_resi,xlab=" ",ylab=" ",main="",type="l",col="red",ylim=c(-15,15))

#model checking
Box.test(garch_ar_resi,10,type="Ljung")
1-pchisq(8.3949,9)
Box.test(garch_ar_resi^2,10,type="Ljung")
1-pchisq(4.0023,9)

predict(garch_ar, n.ahead = 241, trace = FALSE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```


```{r}
garchm = ugarchspec(variance.model=list(model="sGARCH", garchOrder=c(1,1)), 
                    mean.model=list(armaOrder=c(0,0), archm=T, archpow=2, 
                                    include.mean=TRUE))
m_garchm = ugarchfit(spec=garchm,data=train0918)
m_garchm

garchm_res=residuals(m_garchm,standardize=T)

Box.test(garchm_res,10,type="Ljung")
Box.test(garchm_res^2,10,type="Ljung")
```

```{r}
ar_igarch=ugarchspec(
  variance.model=list(model="iGARCH",
                      garchOrder=c(1,1)),
  mean.model=list(armaOrder=c(1,0)))
m_igarch=ugarchfit(spec=ar_igarch,data=train0918)
m_igarch

igarch_res=residuals(m_igarch,standardize=T)

Box.test(igarch_res,10,type="Ljung")
1-pchisq( 8.4284,9)
Box.test(igarch_res^2,10,type="Ljung")
1-pchisq(4.4025,9)
```

```{r}
egarch=ugarchspec(variance.model=list(model="eGARCH"),
                 mean.model=list(armaOrder=c(1,0),include.mean=TRUE),
                 fixed.pars = list(omega = 0))
m_egarch=ugarchfit(spec=egarch,data=train0918)
m_egarch

egarch_res=residuals(m_egarch,standardize=T)

Box.test(egarch_res,10,type="Ljung")
1-pchisq( 8.4069,9)
Box.test(egarch_res^2,10,type="Ljung")
1-pchisq( 6.365,9)

-0.068936/0.128949

fore = ugarchforecast(m_egarch,method = c("Partial", "Full")[1], n.ahead = 241)
fore
#fitted(fore)+ sigma(fore) * sigma(fore)/2
u1 = fitted(fore)+1.96* sigma(fore)
l1 = fitted(fore)-1.96* sigma(fore)

plot(1:241,valid19,type="l",main="daily 2009-2018 AR(1)+EGARCH(1,1) Forecasting", col="black", xlab = "", ylab="")
lines(1:241, fitted(fore), type="l", col="red")
lines(1:241, u1, type="l", col="blue")
lines(1:241, l1, type="l", col="blue")
legend(x="topleft",c("True returns","prediction", "prediction intervals"),col=c("black","red", "blue" ),lty=c(1,1),pch=c(1,1))
```

```{r}
tgarch=garchFit(train0918~arma(1,0)+aparch(1,1),data=train0918,trace=F,delta=2,include.delta=F, include.mean = FALSE)
tgarch
tgarch_res=residuals(tgarch,standardize=T)

Box.test(tgarch_res,10,type="Ljung")
1-pchisq( 8.1742,9)
Box.test(tgarch_res^2,10,type="Ljung")
1-pchisq( 5.8185,9)
```

```{r}
ma=arima(train0918,order=c(0,0,9), fixed = c(NA, 0, 0, 0, 0, 0, 0, 0, NA, NA))
ma

Box.test(ma$residuals,lag=10,type="Ljung")
pv=1-pchisq(12.172,8)
pv#0.1436931

forecast=predict(ma,241)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred+forecast$se*forecast$se
print(sqrt(sum((valid19-E1)^2)/241))

```

```{r}
ar_res = (ma$residuals)^2
acf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
pacf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(ar_res,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(ar_res) #p-value = 0.01
```

```{r}
garch_ma=garchFit(train0918~arma(0, 1)+garch(1,1),data=train0918,trace=F)
summary(garch_ma)
garch_ma_resi=residuals(garch_ma,standardize=T)
plot(garch_ma_resi,xlab=" ",ylab=" ",main="",type="l",col="red",ylim=c(-15,15))

#model checking
Box.test(garch_ma_resi,10,type="Ljung")
1-pchisq( 8.210973,9)
1-pchisq( 4.016546,9)
Box.test(garch_ma_resi^2,10,type="Ljung")
predict(garch_ma, n.ahead = 241, trace = FALSE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```

```{r}
ma_igarch=ugarchspec(
  variance.model=list(model="iGARCH",
                      garchOrder=c(1,1)),
  mean.model=list(armaOrder=c(0,1)))
m_igarch=ugarchfit(spec=ma_igarch,data=train0918)
m_igarch

igarch_res=residuals(m_igarch,standardize=T)

Box.test(igarch_res,10,type="Ljung")
Box.test(igarch_res^2,10,type="Ljung")
1-pchisq( 8.097,9)
1-pchisq( 4.3952,9)
```

```{r}
egarch=ugarchspec(variance.model=list(model="eGARCH"),
                 mean.model=list(armaOrder=c(0,1),include.mean=FALSE) )
m_egarch=ugarchfit(spec=egarch,data=train0918)
m_egarch

egarch_res=residuals(m_egarch,standardize=T)

Box.test(egarch_res,10,type="Ljung")
Box.test(egarch_res^2,10,type="Ljung")
1-pchisq(  7.7722,9)
1-pchisq( 6.7634,9)
-0.074008/0.133416 
```

```{r}
tgarch=garchFit(train0918~arma(0,1)+aparch(1,1),data=train0918,trace=F,delta=2,include.delta=F, include.mean = FALSE)
tgarch
tgarch_res=residuals(tgarch,standardize=T)

Box.test(tgarch_res,10,type="Ljung")
Box.test(tgarch_res^2,10,type="Ljung")
1-pchisq(7.8226,9)
1-pchisq(5.7476,9)
```

```{r}
acf(train0920,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0920,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0920,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0920) #p-value = 0.01
```

```{r}
ar=arima(train0920,order=c(11,0,0), fixed = c(0, 0, 0, 0, 0, NA, NA, 0, 0, NA, NA, NA))
ar

Box.test(ar$residuals,lag=10,type="Ljung")
pv=1-pchisq(7.8601,6)
pv#0.248533

length(valid21)
forecast=predict(ar,219)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred
print(sqrt(sum((valid21-E1)^2)/219))
plot(1:219,valid21,type="l",main="daily 2009-2020 AR(11) Forecasting", col="black", xlab = "", ylab="")
lines(1:219, E1, type="l", col="red")
lines(1:219, U1, type="l", col="blue")
lines(1:219, L1, type="l", col="blue")
legend(x="topleft",lty=c(1,1),pch=c(1,1),c("True returns","prediction"),col=c("black","red"))

```

```{r}
ar_res = (ar$residuals)^2
acf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
pacf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(ar_res,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(ar_res) #p-value = 0.01
```

```{r}
garch_ar=garchFit(train0920~arma(1, 0)+garch(1,1),data=train0920,trace=F)
summary(garch_ar)
garch_ar_resi=residuals(garch_ar,standardize=T)
plot(garch_ar_resi,xlab=" ",ylab=" ",main="",type="l",col="red",ylim=c(-15,15))

#model checking
Box.test(garch_ar_resi,10,type="Ljung")
1-pchisq(11.639,9)
Box.test(garch_ar_resi^2,10,type="Ljung")
1-pchisq(4.3935,9)

predict(garch_ar, n.ahead = 241, trace = FALSE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```

```{r}
garchm = ugarchspec(variance.model=list(model="sGARCH", garchOrder=c(1,1)), 
                    mean.model=list(armaOrder=c(0,0), archm=T, archpow=2, 
                                    include.mean=TRUE))
m_garchm = ugarchfit(spec=garchm,data=train0920)
m_garchm

garchm_res=residuals(m_garchm,standardize=T)

Box.test(garchm_res,10,type="Ljung")
Box.test(garchm_res^2,10,type="Ljung")
1-pchisq(4.3935,9)
1-pchisq(4.3935,9)
```

```{r}
ar_igarch=ugarchspec(
  variance.model=list(model="iGARCH",
                      garchOrder=c(1,1)),
  mean.model=list(armaOrder=c(1,0)))
m_igarch=ugarchfit(spec=ar_igarch,data=train0920)
m_igarch

igarch_res=residuals(m_igarch,standardize=T)

Box.test(igarch_res,10,type="Ljung")
Box.test(igarch_res^2,10,type="Ljung")
1-pchisq(11.071,9)
1-pchisq(4.5693,9)
```

```{r}
egarch=ugarchspec(variance.model=list(model="eGARCH"),
                 mean.model=list(armaOrder=c(1,0),include.mean=TRUE),
                 fixed.pars = list(omega = 0))
m_egarch=ugarchfit(spec=egarch,data=train0920)
m_egarch

egarch_res=residuals(m_egarch,standardize=T)

Box.test(egarch_res,10,type="Ljung")
Box.test(egarch_res^2,10,type="Ljung")
1-pchisq(10.994,9)
1-pchisq(6.6087,9)
-0.087177/0.145566
```

```{r}
tgarch=garchFit(train0920~arma(1,0)+aparch(1,1),data=train0920,trace=F,delta=2,include.delta=F)
tgarch
tgarch_res=residuals(tgarch,standardize=T)

Box.test(tgarch_res,10,type="Ljung")
Box.test(tgarch_res^2,10,type="Ljung")
1-pchisq(11.267,9)
1-pchisq(5.9825,9)

#fitted(fore)+ sigma(fore) * sigma(fore)/2

predict(tgarch, n.ahead = 219, trace = FALSE, mse = c("cond","uncond"),main ="daily 2009-2020 MA(1)+TGARCH(1,1) Forecasting",
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
lines(735:953, valid21, type="l", col="pink")
legend(x="topleft",c("True returns"),col=c("pink" ),lty=c(1,1),pch=c(1,1))
```

```{r}
ma=arima(train0920,order=c(0,0,10), fixed = c(0, 0, 0, 0, 0, NA, NA, 0, NA, NA, NA))
ma

Box.test(ma$residuals,lag=10,type="Ljung")
pv=1-pchisq(4.5196,6)
pv#0.6067261

length(valid21)
forecast=predict(arma,219)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred+forecast$se*forecast$se
print(sqrt(sum((valid21-E1)^2)/219))
```

```{r}
ar_res = (ma$residuals)^2
acf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
pacf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(ar_res,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(ar_res) #p-value = 0.01
```

```{r}
garch_ma=garchFit(train0920~arma(0, 1)+garch(1,1),data=train0920,trace=F)
summary(garch_ma)
garch_ma_resi=residuals(garch_ma,standardize=T)
plot(garch_ma_resi,xlab=" ",ylab=" ",main="",type="l",col="red",ylim=c(-15,15))

#model checking
Box.test(garch_ma_resi,10,type="Ljung")
1-pchisq(11.849,9)
Box.test(garch_ma_resi^2,10,type="Ljung")
1-pchisq(4.4203,9)
predict(garch_ma, n.ahead = 241, trace = FALSE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```

```{r}
ma_igarch=ugarchspec(
  variance.model=list(model="iGARCH",
                      garchOrder=c(1,1)),
  mean.model=list(armaOrder=c(0,1)))
m_igarch=ugarchfit(spec=ma_igarch,data=train0920)
m_igarch

igarch_res=residuals(m_igarch,standardize=T)

Box.test(igarch_res,10,type="Ljung")
Box.test(igarch_res^2,10,type="Ljung")
1-pchisq(11.148,9)
1-pchisq(4.5646,9)
```

```{r}
egarch=ugarchspec(variance.model=list(model="eGARCH"),
                 mean.model=list(armaOrder=c(0,1)),
                 fixed.pars = list(omega = 0))
m_egarch=ugarchfit(spec=egarch,data=train0920)
m_egarch

egarch_res=residuals(m_egarch,standardize=T)

Box.test(egarch_res,10,type="Ljung")
Box.test(egarch_res^2,10,type="Ljung")
1-pchisq(10.829,9)
1-pchisq(6.6351,9)
-0.086580/0.145661
```

```{r}
tgarch=garchFit(train0918~arma(0,1)+aparch(1,1),data=train0918,trace=F,delta=2,include.delta=F, include.mean = FALSE)
tgarch
tgarch_res=residuals(tgarch,standardize=T)

Box.test(tgarch_res,10,type="Ljung")
Box.test(tgarch_res^2,10,type="Ljung")
1-pchisq(7.8226,9)
1-pchisq(5.7476,9)
```

```{r}
arma=arima(train0920,order=c(4,0, 4))
arma

Box.test(arma$residuals,lag=10,type="Ljung")
pv=1-pchisq(18.662,2)
pv#0.1702585
length(valid19)
forecast=predict(arma,219)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred+forecast$se*forecast$se
print(sqrt(sum((valid19-E1)^2)/219))

plot(1:219,valid21,type="l",main="daily 2009-2020 AR(11) Forecasting", col="black", xlab = "", ylab="")
lines(1:219, E1, type="l", col="red")
legend(x="topleft",lty=c(1,1),pch=c(1,1),c("True returns","prediction"),col=c("black","red"))

```


```{r}
weekly <- as.numeric(read.csv("weekly_2009_to_2021.csv",header=T, stringsAsFactors=F)$Close)
plot(weekly,type="l")
weekly_return= diff(log(weekly))*100
plot(weekly_return,type="l")
train0918 = weekly_return[1:523]
valid19 = weekly_return[524:575]
train0920 = weekly_return[1:628]
valid21 = weekly_return[629:676]
```

```{r}
acf(train0918,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0918,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0918,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0918) #p-value = 0.01
```

```{r}
acf(train0918^2,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0918^2,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0918^2,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0918^2) #p-value = 0.01
```

```{r}
train0918_diff = diff(train0918, 12)
acf(train0918_diff,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0918_diff,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0918_diff,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0918_diff) #p-value = 0.01
```

```{r}
arma = arima(train0918,c(4, 0, 4), fixed = c(0, 0, 0, NA, 0, 0, 0, NA, NA))
arma

Box.test(arma$residuals,lag=10,type="Ljung")
pv=1-pchisq(10.301,8)
pv#0.244532

length(valid19)
forecast=predict(arma,52)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred
print(sqrt(sum((valid19-E1)^2)/52))
plot(1:52,valid19,type="l",main="weekly 2009-2018 ARMA(4,4) Forecasting", ylim=c(-7,7), col="black", xlab = "", ylab="")
lines(1:52, E1, type="l", col="red")
lines(1:52, U1, type="l", col="blue")
lines(1:52, L1, type="l", col="blue")
legend(x="topleft",lty=c(1,1),pch=c(1,1),c("True returns","prediction"),col=c("black","red"))
```

```{r}
ar_res = (arma$residuals)^2
acf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
pacf(ar_res,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(ar_res,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(ar_res) #p-value = 0.01
```

```{r}
garch_ma=garchFit(train0918~garch(1,1),data=train0918,trace=F)
summary(garch_ma)
garch_ma_resi=residuals(garch_ma,standardize=T)
plot(garch_ma_resi,xlab=" ",ylab=" ",main="",type="l",col="red",ylim=c(-15,15))

#model checking
Box.test(garch_ma_resi,10,type="Ljung")
Box.test(garch_ma_resi^2,10,type="Ljung")
predict(garch_ma, n.ahead = 241, trace = FALSE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```

```{r}
ma_igarch=ugarchspec(
  variance.model=list(model="iGARCH",
                      garchOrder=c(1,1)),
  mean.model=list(armaOrder=c(0,0)))
m_igarch=ugarchfit(spec=ma_igarch,data=train0918)
m_igarch
#LogLikelihood : -1179.769 only garch
#LogLikelihood : -1178.414 arma 1 1
igarch_res=residuals(m_igarch,standardize=T)

Box.test(igarch_res,10,type="Ljung")
Box.test(igarch_res^2,10,type="Ljung")
```

```{r}
egarch=ugarchspec(variance.model=list(model="eGARCH"),
                 mean.model=list(armaOrder=c(0,0)),
                 fixed.pars = list(alpha1 = 0))
m_egarch=ugarchfit(spec=egarch,data=train0918)
m_egarch

egarch_res=residuals(m_egarch,standardize=T)

Box.test(egarch_res,10,type="Ljung")
Box.test(egarch_res^2,10,type="Ljung")
fore = ugarchforecast(m_egarch,method = c("Partial", "Full")[1], n.ahead = 52)
fore
#fitted(fore)+ sigma(fore) * sigma(fore)/2
u1 = fitted(fore)+1.96* sigma(fore)
l1 = fitted(fore)-1.96* sigma(fore)

plot(1:52,valid19,type="l",main="weekly 2009-2018 EGARCH(1,1) Forecasting", col="black", xlab = "", ylab="")
lines(1:52, fitted(fore), type="l", col="red")
lines(1:52, u1, type="l", col="blue")
lines(1:52, l1, type="l", col="blue")
legend(x="topleft",c("True returns","prediction", "prediction intervals"),col=c("black","red", "blue" ),lty=c(1,1),pch=c(1,1))
```

```{r}
tgarch=garchFit(train0918~aparch(2,2),data=train0918,trace=F,delta=2,include.delta=F, include.mean = FALSE, fixed.pars = list(alpha1=0, gamma1=0, beta1=0))
tgarch
tgarch_res=residuals(tgarch,standardize=T)

Box.test(tgarch_res,10,type="Ljung")
Box.test(tgarch_res^2,10,type="Ljung")
```

```{r}
sarma = arima(train0918,c(4, 0, 4),seasonal = list(order = c(2, 0, 2),period = 4))
sarma

Box.test(sarma$residuals,lag=10,type="Ljung")
pv=1-pchisq(10.301,8)
pv

length(valid19)
forecast=predict(sarma,52)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred+forecast$se*forecast$se
print(sqrt(sum((valid19-E1)^2)/52))
```


```{r}
acf(train0920,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0920,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0920,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0920) #p-value = 0.01
```

```{r}
acf(train0920^2,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0920^2,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0920^2,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0920) #p-value = 0.01
```

```{r}
ar = arima(train0920,c(8, 0, 0), fixed = c(0, 0, 0, 0, 0, 0, 0, NA, NA))
ar

Box.test(ar$residuals,lag=10,type="Ljung")
pv=1-pchisq(11.879,9)
pv

length(valid21)
print(sqrt((sum(valid21[1:45]-E1)^2)/45))
forecast=predict(ar,45)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred
print(sqrt((sum(valid21[1:45]-E1)^2)/45))

plot(1:45,valid21[1:45],type="l",main="weekly 2009-2020 AR(8) Forecasting", ylim=c(-10,10), col="black", xlab = "", ylab="")
lines(1:45, E1, type="l", col="red")
lines(1:45, U1, type="l", col="blue")
lines(1:45, L1, type="l", col="blue")
legend(x="topleft",lty=c(1,1),pch=c(1,1),c("True returns","prediction"),col=c("black","red"))
```

```{r}
ma = arima(train0920,c(0, 0, 8), fixed = c(0, 0, 0, 0, 0, 0, 0, NA, NA))
ma

Box.test(ma$residuals,lag=10,type="Ljung")
pv=1-pchisq(11.729,9)
pv
forecast=predict(ma,45)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred
print(sqrt((sum(valid21[1:45]-E1)^2)/45))

plot(1:45,valid21[1:45],type="l",main="weekly 2009-2020 MA(8) Forecasting", ylim=c(-10,10), col="black", xlab = "", ylab="")
lines(1:45, E1, type="l", col="red")
lines(1:45, U1, type="l", col="blue")
lines(1:45, L1, type="l", col="blue")
legend(x="topleft",lty=c(1,1),pch=c(1,1),c("True returns","prediction"),col=c("black","red"))
```

```{r}
arma = arima(train0920,c(4, 0, 4), fixed = c(0, 0, 0, NA, 0, 0, 0, NA, NA))
arma

Box.test(arma$residuals,lag=10,type="Ljung")
pv=1-pchisq(12.015,8)
pv
forecast=predict(arma,45)
U1=forecast$pred +1.96 * forecast$se
L1=forecast$pred - 1.96 * forecast$se
E1=forecast$pred+forecast$se*forecast$se
print(sqrt((sum(valid21[1:45]-E1)^2)/45))
```
```{r}
garch_ar=garchFit(train0920~arma(0, 0)+garch(1,1),data=train0920,trace=F)
summary(garch_ar)
garch_ar_resi=residuals(garch_ar,standardize=T)
plot(garch_ar_resi,xlab=" ",ylab=" ",main="",type="l",col="red",ylim=c(-15,15))

#model checking
Box.test(garch_ar_resi,10,type="Ljung")
Box.test(garch_ar_resi^2,10,type="Ljung")


predict(garch_ar, n.ahead = , trace = FALSE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```


```{r}
garchm = ugarchspec(variance.model=list(model="sGARCH", garchOrder=c(1,1)), 
                    mean.model=list(armaOrder=c(0,0), archm=T, archpow=2, 
                                    include.mean=TRUE))
m_garchm = ugarchfit(spec=garchm,data=train0920)
m_garchm

garchm_res=residuals(m_garchm,standardize=T)

Box.test(garchm_res,10,type="Ljung")
Box.test(garchm_res^2,10,type="Ljung")
```

```{r}
ar_igarch=ugarchspec(
  variance.model=list(model="iGARCH",
                      garchOrder=c(1,1)),
  mean.model=list(armaOrder=c(0,0)))
m_igarch=ugarchfit(spec=ar_igarch,data=train0920)
m_igarch

igarch_res=residuals(m_igarch,standardize=T)

Box.test(igarch_res,10,type="Ljung")
Box.test(igarch_res^2,10,type="Ljung")
```

```{r}
egarch=ugarchspec(variance.model=list(model="eGARCH"),
                 mean.model=list(armaOrder=c(0,0),include.mean=FALSE),
                 fixed.pars = list(omega = 0))
m_egarch=ugarchfit(spec=egarch,data=train0920)
m_egarch

egarch_res=residuals(m_egarch,standardize=T)

Box.test(egarch_res,10,type="Ljung")
Box.test(egarch_res^2,10,type="Ljung")
```

```{r}
tgarch=garchFit(train0918~arma(0,0)+aparch(1,1),data=train0920,trace=F,delta=2,include.delta=F, include.mean = TRUE)
tgarch
tgarch_res=residuals(tgarch,standardize=T)

Box.test(tgarch_res,10,type="Ljung")
Box.test(tgarch_res^2,10,type="Ljung")
length(valid21)
predict(tgarch, n.ahead =45 , trace = FALSE, mse = c("cond","uncond"),main ="daily 2009-2020 MA(1)+TGARCH(1,1) Forecasting",
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
lines(159:203, valid21[1:45], type="l", col="pink")
legend(x="topleft",c("True returns"),col=c("pink" ),lty=c(1,1),pch=c(1,1))
```


```{r}
monthly <- as.numeric(read.csv("monthly_2009_to_2021.csv",header=T, stringsAsFactors=F)$Close)
plot(monthly,type="l")
monthly_return= diff(log(monthly))*100
plot(monthly_return,type="l")
train0918 = monthly_return[1:121]
valid19 = monthly_return[122:133]
train0920 = monthly_return[1:145]
valid21 = monthly_return[146:157]
```

```{r}
acf(train0918,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0918,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0918,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0918) #p-value = 0.01
```


```{r}
acf(train0918^2,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0918^2,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0918^2,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0918^2) #p-value = 0.01
```

```{r}
acf(train0920^2,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0920^2,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0920^2,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0920^2) #p-value = 0.01
```

```{r}
acf(train0920,20,main="",col="red",ylim=c(-0.2,1))
pacf(train0920,20,main="",col="red",ylim=c(-0.2,1))
print("if p.value < 0.05 not white noise else white noise")
Box.test(train0920,lag=10,type="Ljung")
print("if p.value < 0.05 stationary else not stationary")
tseries::adf.test(train0920) #p-value = 0.01
```


```{r}
garchm = ugarchspec(variance.model=list(model="sGARCH", garchOrder=c(0,1)), 
                    mean.model=list(armaOrder=c(0,0), archm=T, archpow=2, 
                                    include.mean=TRUE),
                    fixed.pars = list(omega=0))
m_garchm = ugarchfit(spec=garchm,data=train0918)
m_garchm

garchm_res=residuals(m_garchm,standardize=T)

Box.test(garchm_res,10,type="Ljung")
Box.test(garchm_res^2,10,type="Ljung")
```


```{r}
garch_ar=garchFit(train0920~arma(0, 0)+garch(1,0),data=train0920,trace=F)
summary(garch_ar)
garch_ar_resi=residuals(garch_ar,standardize=T)
plot(garch_ar_resi,xlab=" ",ylab=" ",main="",type="l",col="red",ylim=c(-15,15))

#model checking
Box.test(garch_ar_resi,10,type="Ljung")
Box.test(garch_ar_resi^2,10,type="Ljung")

predict(garch_ar, n.ahead = 12, trace = FALSE, mse = c("cond","uncond"),
        plot=TRUE, nx=NULL, crit_val=NULL, conf=NULL)
```




```{r}
egarch=ugarchspec(variance.model=list(model="eGARCH"),
                 mean.model=list(armaOrder=c(0,0),include.mean=FALSE),
                 fixed.pars = list(omega = 0))
m_egarch=ugarchfit(spec=egarch,data=train0920)
m_egarch

egarch_res=residuals(m_egarch,standardize=T)

Box.test(egarch_res,10,type="Ljung")
Box.test(egarch_res^2,10,type="Ljung")
```

```{r}
tgarch=garchFit(train0918~arma(0,0)+aparch(1,1),data=train0920,trace=F,delta=2,include.delta=F, include.mean = TRUE)
tgarch
tgarch_res=residuals(tgarch,standardize=T)

Box.test(tgarch_res,10,type="Ljung")
Box.test(tgarch_res^2,10,type="Ljung")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
